Predictive Modeling of I/O Characteristics \\ in High Performance Computing Systems

### 2017-11-12 HPC_Paper/paper.tex
Working on paper, deleted all test data folders for recreation on pawnee.

Where $s$ is the iteration number, $B_l(x)$ and $B_k(x)$ are some
previously generated basis functions, $c, v \in \mathbb{R}$, and $x_i$
with $0 < i \leq d$ is the $i^{th}$ component (1 indexed) of input
vector $x$. After iteratively constructing a model, MARS then
iteratively removes basis functions that do not contribute to goodness
of fit. In effect, MARS creates a locally component-wise linear
approximation of the data that is $C^0$. The overall computational
complexity of Fast MARS is $\mathcal{O}(n d m^3)$ where $m$ is a user
selected value that is the maximum complexity of the model in terms of
the number of underlying basis functions. This paper uses a default
max number of basis functions of $n$, however with larger datasets ($n
> 1000$)this value would need to be reduced.

@@

Where $W_l$ is the $i$ by $j$ weight matrix of layer $l$ and the max
function is applied element-wise to the resulting vector. In this
form, the multi-layer perceptron (MLP) produces a locally linear model
of the input data that is $C^0$. The computational complexity of
training a multi-layer perceptron is approximately $\mathcal{O}(n d
m)$ where $m$ is a constant determined by a linear function of the
sizes of the layers of the network and the convergence stopping
criteria of the BFGS minimization used for finding weights. This paper
uses a single hidden layer with 100 nodes, ReLU activation, and BFGS
for training.

\subsubsection{Support Vector Regressor}
Support vector machines are a common tool used in machine learning
classification tasks that can be adapted for the purpose of regression
\cite{basak2007support}. The mathematical formalisms for exactly how
to build a support vector regressor (SVR) are beyond the scope of this
summary, but the core of the technique solves an optimization problem
of the form

$$ \text{Minimize } \bigg\{ \frac{1}{2}\sum_{i=1}^{n}\sum_{j=1}^{n}
a_i a_j K(x_i, x_j) + \epsilon \sum_{i=1}^{n} a_i - \sum_{i=1}^{n} y_i
a_i \bigg\} $$

$$ \text{Subject to } \sum_{i=1}^{n}a_i = 0 \text{ } \text{ and }
\text{ } a_i \in [0,C] $$

Where $K$ is the selected kernel function, $a \in \mathbb{R}^n$ is the
solved coefficient vector, and $\epsilon$ is the error tolerance.

\subsection{Interpolation}
\subsubsection{Delaunay}
\subsubsection{Linear Shepard}

>>>>

Where $s$ is the iteration number, $B_l(x)$ and $B_k(x)$ are some
previously generated basis functions, $c, v \in \mathbb{R}$, and $x_i$
with $0 < i \leq d$ is the $i^{th}$ component (1 indexed) of input
vector $x$. After iteratively constructing a model, MARS then
iteratively removes basis functions that do not contribute to goodness
of fit. In effect, MARS creates a locally component-wise linear
approximation of the data that is $C^0$. The overall computational
complexity of Fast MARS is $\mathcal{O}(n d m^3)$ where $m$ is a user
selected value that is the maximum complexity of the model in terms of
the number of underlying basis functions. This paper uses an Earth
implementation of MARS \cite{rudy2017pyearth} with a max number of
basis functions of $n$, however with larger datasets ($n > 1000$) this
value would need to be reduced.

@@

Where $W_l$ is the $i$ by $j$ weight matrix of layer $l$ and the max
function is applied element-wise to the resulting vector. In this
form, the multi-layer perceptron (MLP) produces a locally linear model
of the input data that is $C^0$. The computational complexity of
training a multi-layer perceptron is approximately $\mathcal{O}(n d
m)$ where $m$ is a constant determined by a linear function of the
sizes of the layers of the network and the convergence stopping
criteria of the BFGS minimization used for finding weights. This paper
uses the scikit-learn MLP regressor \cite{scikit-learn} with a single
hidden layer with 100 nodes, ReLU activation, and BFGS for training.

\subsubsection{Support Vector Regressor}
Support vector machines are a common tool used in machine learning
classification tasks that can be adapted for the purpose of regression
\cite{basak2007support}. The mathematical formalisms for exactly how
to build a support vector regressor (SVR) are beyond the scope of this
summary, but the resulting functional fit is of the form

$$ f(x) : \mathbb{R}^d \rightarrow \mathbb{R} = \sum_{i=1}^{n}a_i
K(x,x_i) $$

%% $$ \text{Minimize } \bigg\{ \frac{1}{2}\sum_{i=1}^{n}\sum_{j=1}^{n}
%% a_i a_j K(x_i, x_j) + \epsilon \sum_{i=1}^{n} a_i - \sum_{i=1}^{n} y_i
%% a_i \bigg\} $$

%% $$ \text{Subject to } \sum_{i=1}^{n}a_i = 0 \text{ } \text{ and }
%% \text{ } a_i \in [0,C] $$

Where $K$ is the selected kernel function, $a \in \mathbb{R}^n$ is the
solved coefficient vector, and $\epsilon$ is the error tolerance. The
SVR is always fitting a linear function, however the kernel mapping of
the data can be non-linear to create non-linear fits. The
computational complexity of the SVR minimization (for the
implementation used) is $\mathcal{O}(n^2dm)$ with $m$ being a constant
determined by the minimization convergence criteria. This paper uses
the scikit-learn SVR \cite{scikit-learn} with a polynomial kernel
function.

\subsection{Interpolation}

\subsubsection{Delaunay}
\subsubsection{Linear Shepard}
